\emph{On Logics Extended with Embedding-Closed Quantifiers}

### 2020-11-07 paper.tex
Shorten more lines
Generalize the antichain lemma to interpretations

In this subsection, we will consider logics $\mathcal{L}_{\infty\omega}^m$
(the restriction of $\mathcal{L}_{\infty\omega}$ to formulas that use at most
$m$ variables) extended with finite number of em\-bed\-ding-closed quantifiers
of finite width.
We will show that in a countably infinite chain of quasi-homogeneous structures
of finite relational vocabulary, a formula of such a logic is eventually
equivalent to a quantifier-free formula.
This will allow us to demonstrate, among other things, that certain properties
of finite structures are not definable in such a logic.

@@

>>>>

In this subsection, we will consider logics $\mathcal{L}_{\infty\omega}^m$
(the restriction of $\mathcal{L}_{\infty\omega}$ to formulas that use at most
$m$ variables) extended with finite number of em\-bed\-ding-closed quantifiers
of finite width.
We will show that in a countably infinite chain of interpretations of 
quasi-homogeneous structures
of finite relational vocabulary, a formula of such a logic is eventually
equivalent to a quantifier-free formula.
This will allow us to demonstrate, among other things, that certain properties
of finite structures are not definable in such a logic.

@@

\begin{corollary}\label{shrinking_interpr}
Let $\tau$ and $\sigma$ be finite relational vocabularies and
$(\Psi, (\psi_R)_{R \in \sigma})$ an 
$\mathcal{L}_{\infty \omega}(\mathcal{Q}_{\emb})$-interpretation of $\sigma$ in
$\tau$.
Let $\mathcal{H}$ be the class of all finite homogeneous $\tau$-structures and
\[
	\Psi(\mathcal{H}) = \{\Psi(\mathfrak{A}) \colon \mathfrak{A} \in \mathcal{H}\}.
\]
Then all antichains of structures of $\Psi(\mathcal{H})$ are finite.
\end{corollary}
\begin{proof}
Assume to the contrary that there is a countably infinite antichain
\[
	\Psi(\mathfrak{A}_0),\ \Psi(\mathfrak{A}_1),\ \dots
\]
with all $\mathfrak{A}_i \in \mathcal{H}$.
There are natural numbers $i_0$, $i_1$, $\dots$ such that 
$\mathfrak{A}_{i_j} \leq \mathfrak{A}_{i_{j + 1}}$ for all $j < \omega$
because otherwise we would be able to construct an infinite antichain of 
homogeneous structures which contradicts Lemma \ref{shrinking}.
By Corollary \ref{finite2}, since $\sigma$ is finite, there is $k < \omega$
such that 
\[
	\mathfrak{A}_k, \overline{a} \vDash \psi_R \Leftrightarrow
	\mathfrak{A}_{k + 1}, \overline{a} \vDash \psi_R
\]
for all $R \in \sigma$ and $\overline{a} \in A_k^{\ar(R)}$.
Thus, since $\mathfrak{A}_k \leq \mathfrak{A}_{k + 1}$, we have
$\Psi(\mathfrak{A}_k) \leq \Psi(\mathfrak{A}_{k + 1})$, contradiction.
\end{proof}
